POMDP comparisons across sigma_m, sigma_g

### 2017-10-02 appendix/appendixB.Rmd
define f

```{r}
# devtools::install_github("boettiger-lab/sarsop")  ## install package first if necessary.
library(sarsop)       # the main POMDP package
library(tidyverse)    # for munging and plotting
library(parallel)
options(mc.cores = 6) # Reserve ~ 10 GB per core
log_dir <- "pomdp_intro"

## Classic Graham-Schaefer. Note that recruitment occurs *before* harvest
f <- function(x, h){ 
  x + x * r * (1 - x / K) - pmin(x,h)
}
reward_fn <- function(x,h) pmin(x,h)
discount <- 1

## Discretize space
states <- seq(0,4, length=150)
actions <- states
observations <- states

## All parameter values combinations for which we want solutions
meta <- expand.grid(species = pars$species, 
                    sigma_m = c(0, 0.1, 0.2),
                    stringsAsFactors = FALSE) %>%
  left_join(pars)

## Create the models
models <- 
  parallel::mclapply(1:dim(meta)[1], 
                     function(i){
                       fisheries_matrices(
                         states = states,
                         actions = actions,
                         observed_states = observations,
                         reward_fn = reward_fn,
                         f = f,
                         sigma_g = meta[i,"sigma_g"][[1]],
                         sigma_m = meta[i,"sigma_m"][[1]],
                         noise = "normal")
                     })

@@

>>>>

```{r}
# devtools::install_github("boettiger-lab/sarsop")  ## install package first if necessary.
library(sarsop)       # the main POMDP package
library(tidyverse)    # for munging and plotting
library(parallel)
options(mc.cores = 6) # Reserve ~ 10 GB per core
log_dir <- "pomdp_intro"
```

```{r}
## Classic Graham-Schaefer. Note that recruitment occurs *before* harvest
gs <- function(r,K){
  function(x, h){ 
    x + x * r * (1 - x / K) - pmin(x,h)
  }
}
reward_fn <- function(x,h) pmin(x,h)
discount <- 1
```

## Discretize space

Note that the large values of $K$ require we carry the numerical grid out further.

```{r}
states <- seq(0,4, length=150)
actions <- states
observations <- states
```

## All parameter values combinations for which we want solutions

```{r}
meta <- expand.grid(species = pars$species, 
                    sigma_m = c(0, 0.1, 0.2),
                    stringsAsFactors = FALSE) %>%
  left_join(pars)
meta
```

## Create the models

```{r}
models <- 
  parallel::mclapply(1:dim(meta)[1], 
                     function(i){
                       fisheries_matrices(
                         states = states,
                         actions = actions,
                         observed_states = observations,
                         reward_fn = reward_fn,
                         f = gs(meta[i, "r"][[1]], meta[i, "K"][[1]]),
                         sigma_g = meta[i,"sigma_g"][[1]],
                         sigma_m = meta[i,"sigma_m"][[1]],
                         noise = "normal")
                     })

@@

## Comparison to the static models

```{r eval=FALSE}
## A generic routine to find stock size (x) which maximizes 
## growth rate (f(x,0) - x, where x_t+1 = f(x_t))

f <- gs(pars[i,"r"][[1]], pars[i, "K"][[1]])

S_star <- optimize(function(x) -f(x,0) + x / discount, 
                   c(0, 2*K))$minimum

B_MSY <- S_star
MSY <- f(B_MSY,0) - B_MSY

F_MSY <- MSY / B_MSY  
F_PGY = 0.8 * F_MSY

policies <- list(
  det = map_int(pmax(f(states,0) - S_star,0), ~ which.min(abs(actions - .x))),
  msy = map_int(states, ~ which.min(abs(actions - .x * F_MSY))),
  pgy = map_int(states, ~ which.min(abs(actions - .x * F_PGY))) )
```
